\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
added stuff about E6SSM problems.  We cannot keep it in this form though. But wnated to put it in temporarily to help explain to Alex and Jae-hyeon.

The modular design of FlexibleSUSY allows solver for the boudary

>>>>

For experienced users the clear code structure also allows the
possibility of direct adaption of the code.  For example in the case
of the E6SSM we observed that for some points the presence of new
Yuwawas had a big impact on the RGEs for the VEVS.  When the user
chooses to set these Yukawas at the GUT scale, then on the initial run
up to the GUT scale they will be set to zero.  As a result the VEV
RGEs on the run up are quite different to the VEV RGEs on the run down
so that the VEVs used at the SUSY scale are far from the correct
values and this can create an instability leading eventually to
non-perturbative in the couplings.  This can be fixed by adapting the
algorithm so that thge VEVs are stored at the SUSY scale.  However a
simpler, if less clean, fix is to directly modify the generated code
by adding three lines to the file
\code{<model>_two_scale_susy_parameters.cpp} just before the beta
functions are returned in method
\code{<model>_susy_parameters::calc_beta()}.

\code{ 
if(get_scale()  > 3.0e3) beta_vd =0;
if(get_scale()  > 3.0e3) beta_vu =0;
if(get_scale()  > 3.0e3) beta_vs =0;
return E6SSMnew_susy_parameters(get_scale(), get_loops(), get_thresholds(), input,
beta_Yd, beta_Ye, beta_Kappa, beta_Lambda12, beta_Lambdax, beta_Yu, beta_MuPr, beta_g1, beta_g2, beta_g3, beta_g1p, beta_vd, beta_vu, beta_vs);
}

In addition modular design of FlexibleSUSY allows solver for the boundary
